|

### 2025-04-25 output/seminar-slideshow.qmd
Add oblique basis representation

@@

>>>>

## Representación gráfica completa

@@

plot_orth <- plot_orth +
  scale_color_manual(values = ITEMS_PALETTE) +
  theme(
    axis.ticks       = element_blank(),
    legend.title     = element_blank(),
    panel.grid.minor = element_blank()
  )

plot_oblique <- plot_oblique +
  scale_color_manual(values = ITEMS_PALETTE, guide = NULL) +
  theme(axis.ticks = element_blank())
